% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@sudo.ws> http://www.sudo.ws/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Nicolas S. Montanaro}  & (203) 505-0205 \\
39-74 44th St Flr 2 &  \href{mailto:mail@nicolasmontanaro.com}{mail@nicolasmontanaro.com} \\
Sunnyside, NY 11104& \href{https://nicolasmontanaro.com}{nicolasmontanaro.com}\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Work experience}
\begin{itemize}
	\item
	\ressubheading{Sonara Health}{Remote}{Senior software engineer}{June 2022 - present}
	\begin{itemize}
		\resitem{Designed and implemented a relational database structure to accurately record and analyze user activity history.}
		\resitem{Planned and executed a framework for collecting patient demographic information.}
		\resitem{Bridged our web application to Zendesk in an effort to shift operational burden from opioid treatment centers to our internal customer success team.}
		\resitem{Collaborated with team to rapidly patch a critical production bug, minimizing service outage impact.}
		\resitem{Developed a custom measurement-based care framework, combining UI components, database designs, and data collection standards, enabling the collection of voluntary patient information aligned with Sonara's specific requirements as an alternative to off-the-shelf solutions.}
	\end{itemize}
\item
	\ressubheading{Foyer, Inc. (defunct)} {Trumbull, CT}{Technology director}{May 2017 - June 2022}
	\begin{itemize}
		\resitem{Assumed responsibility for overall direction and technical implementation for the Foyer ML platform as the company grew from 2 employees to 8.}
		\resitem{Planned, designed, implemented and maintained a datastore and REST API for real estate metadata.}
		\resitem{Designed and programmed an iOS application for real estate listing creation and automatic feature detection. Feature extraction was performed in real-time as a video of a home was taken.}
	\end{itemize}
\item 
	\ressubheading{Recurse Center}{New York, NY}{Participant}{February 2018 - May 2018}
	\begin{itemize}
		\resitem{Participated in a self-directed, project-based programming retreat, where I created a Game Boy emulator in Go and delivered a presentation on the implementation details.}
	\end{itemize}
\item 
	\ressubheading{Intel}{Santa Clara, CA}{Software application engineer}{January 2015 - December 2015}
	\begin{itemize}
		\resitem{Analyzed the performance of 3D camera hardware and software on Intel architecture prior to release.}
		\resitem{Developed and tested mobile performance analysis tools for Android, iOS, and Windows-based tablets for Intel lab
		personnel.}
		\resitem{Received an award for the identification and resolution of proprietary software issues which resulted in the on-time delivery of a performance
		monitoring tool to Intel labs.}
	\end{itemize}
\end{itemize}

\resheading{Open source projects}

\begin{itemize}
\item 
	\ressubheading{Halken}{}{Go}{\href{https://github.com/99z/halken}{github.com/99z/halken}}
	\begin{itemize}
		\resitem{Halken is a Game Boy emulator written in Go.}
		\resitem{Created as an exercise in low-level programming and to gain a better understanding of computer architecture while at the Recurse Center.}
	\end{itemize}
\item 
	\ressubheading{Independent study in code clone detection techniques}{}{Java}{\href{https://nicolasmontanaro.com/indstudy.pdf}{nicolasmontanaro.com/indstudy.pdf}}
	\begin{itemize}
		\resitem{Implemented a simplified version of the GPLAG algorithm for code clone detection.}
		\resitem{Compared GPLAG against widely-used tools for plagiarism detection in student code submissions.}
		\resitem{Benchmarked and analyzed tokenization vs. subgraph isomorphism detection techniques for code clone detection.}
	\end{itemize}
\end{itemize}

\resheading{Education}
\begin{itemize}
	\item \ressubheading{Rochester Institute of Technology}{Rochester, NY}{Computer Science}{August 2012 - May 2017}
\end{itemize}

% \resheading{Skills}

% \begin{description}
% \item[Languages:]
% C/C{}\verb!++!, C{}\verb!#!, Perl, Java, Unix Shell, Sed, Awk
% \item[Operating Systems:]
% Linux, OpenBSD, FreeBSD, Mac OS X, {\sc UNIX}
% \item[Security:]
% Extensive experience writing secure code and auditing code for security-related errors
% \item[Miscellaneous:]
% Excellent troubleshooting and debugging skills
% \end{description}

\end{document}
